---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cnd

<!-- badges: start -->
[![R-CMD-check](https://github.com/jmbarbone/cnd/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jmbarbone/cnd/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jmbarbone/cnd/graph/badge.svg)](https://app.codecov.io/gh/jmbarbone/cnd)
<!-- badges: end -->

The goal of `{cnd}` is to provide easy, customized classes for `conditions`.
This makes setting up custom conditions quick and more useful.

## Installation

You can install the development version of `{cnd}` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("jmbarbone/cnd")
```

## Example

`condition()` creates a `cnd::condition_generator` that can generate the condition when called.

```{r}
library(cnd)
bad_value <- condition("bad_value", message = "Value has to be better")

bad_value
bad_value()

foo <- function(x) {
  if (x < 0) {
    stop(bad_value())
  }
  x
}

try(foo(-1))
```

`cnd::condition_generator`s can also take parameters that are used in creating a custom message.

```{r}
bad_value2 <- condition(
  "bad_value2",
  message = function(x) sprintf("Value '%s' is no good", format(x))
)

bad_value2
bad_value2(0)

foo <- function(x) {
  if (x < 0) {
    stop(bad_value2(x))
  }
  x
}

try(foo(-1L))
```

## Registration

Conditions can be assigned into objects within your package by adding one line to your package.
This is probably best in a file like `R/zzz.R` that can be run at the end of your package load, before the namespace is locked.

```r
cnd::register_conditions(pkgname)
```

Once that is done, your functions will have a `cnd::conditioned_function` class added to them and print the conditions you have linked.

```{r}
#| include: false
# ignoring registration for now
condition <- cnd::condition
formals(condition)["register"] <- FALSE
```


```{r}
condition(
  "an_example",
  package = "pkg",
  help = "more info",
  exports = "fun"
)
```

```r
pkg::fun
#> function () 
#> {
#>     # nonsense example
#> }
#> <environment: 0x000000000000>
#> <condition(s): pkg:error/an_example>
```

## Documentation

`cnd_document()` will create a `.Rd` file for all conditions you have assigned to your package.
Simply run the command when developing to generate a file listing all conditions.

```r
cnd::cnd_document()
```

## Retrieval

You can retrieve any `conditions` that are created with `conditions()`.
By default this will list all `conditions` loaded, but can be filtered by specific packages.

```{r}
conditions("cnd")
```
